Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/discussion.tex

>>>>

Variational Bayes has been the predominant estimation approach applied to sLDA models.  Hierarchical probit regression makes for tractable Markov chain Monte Carlo SLDA inference, a benefit that should extend to other sLDA models should probit regression be used for response variable prediction there too.

The results in Figures~\ref{fig:1a} and \ref{fig:1b} suggest that in most cases it is better to do full joint estimation of HSLDA.  In alternative interpretation of the same results is that if one is more sensitive to the performance gains that result from exploiting the structure of the labels then one can, in an engineering sense, get nearly as much gain in label prediction performance by first fitting LDA and then fitting a hierarchical probit regression.  There are applied settings in which this could be advantageous.

### 2011-06-02 paper/introduction.tex

There are several challenges entailed in incorporating a hierarchy of labels.
Given a large set of potential labels (often thousands), each instance has only
a small number of labels associated to it. There are no negative labeling
present in the data naturally, and the absence of a label cannot always be
interpreted as a negative labeling.

@@

Our work operates within the framework of topic modeling. Our approach learns
topic models of the underlying data and labeling strategies in a joint model,
while leveraging the hierarchical structure of the labels. In particular, we
extend supervised latent Dirichlet allocation (sLDA)~\cite{BleiMcAuliffe2008}
to take advantage of hierarchical supervision. We hypothesize that hierarchical
label information provides more information about labeling than considering
unstructured labels.

We demonstrate our model on large, real-world datasets in the clinical and web
retail domains. We observe that hierarchical information is valuable when
incorporated into the learning and improves our primary goal of multi-label
classification. %in two ways

>>>>

There are several challenges entailed in incorporating a hierarchy of labels
into the model. Given a large set of potential labels (often thousands), each
instance has only a small number of labels associated to it. There are no
naturally occurring negative labeling in the data, and the absence of a label
cannot always be interpreted as a negative labeling.

@@

Our work operates within the framework of topic modeling. Our approach learns
topic models of the underlying data and labeling strategies in a joint model,
while leveraging the hierarchical structure of the labels. For the sake of
simplicity, we focus on ISA hierarchies, but the model can be
applied to other hierarchies. We extend supervised latent Dirichlet
allocation (sLDA)~\cite{BleiMcAuliffe2008} to take advantage of hierarchical
supervision. We propose an efficient way to incorporate hierarchical
information into the model. We hypothesize that the context of labels within
the hierarchy provides valuable information about labeling.

We demonstrate our model on large, real-world datasets in the clinical and web
retail domains. We observe that hierarchical information is valuable when
incorporated into the learning and improves our primary goal of multi-label
classification. Our results show that a joint, hierarchical model outperforms a
classification with unstructured labels as well as a disjoint model, where the
topic modeling and the hierarchical classification are carried out
independently of each other.
